Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-28 paper_comparison/appendix.Rmd
modify the last plot

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, "Propotion of lineups with $p$-value < 0.05 but adjusted $p$-value > 0.05", "Propotion of lineups with $p$-value > 0.05 but adjusted $p$-value < 0.05")) %>%
  rename(multiplier = modified) %>%
  mutate(n = paste0(round(n/279 * 100, 2), "\\%")) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "sensitivity", 
                    escape = FALSE,
                    caption = "Change of rejection decision because of the modification of $\\hat{\\alpha}$.")
```

@@

map_df(seq(1, 11, 2), ~eval_n(.x, 1)) %>%
  select(-boot_id) %>%
  nest(c(effect_size, reject, offset0)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-data, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = factor(n_eval)),
            size = 1) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

@@

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 4) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))
```

```{r}
reset_diff_dat %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = as.factor(as.integer(name))),
            size = 1) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 1) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))
```

```{r}
reset_diff_dat %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = as.factor(as.integer(name))),
            size = 1) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

>>>>

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, 'Proportion of lineups transforms to "not reject"', 'Proportion of lineups transforms to "reject"')) %>%
  rename(multiplier = modified) %>%
  mutate(n = paste0(round(n/279 * 100, 2), "\\%")) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "sensitivity", 
                    escape = FALSE,
                    caption = "Change of rejection decision because of the modification of $\\hat{\\alpha}$.")
```

@@

map_df(seq(1, 11, 2), ~eval_n(.x, 1)) %>%
  select(-boot_id) %>%
  nest(c(effect_size, reject, offset0)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-data, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = factor(n_eval)),
            size = 1) +
  labs(col = "Number of evalutaions") +
  xlab(expression(log[e] (Effect_size))) +
  theme_light() +
  scale_color_brewer(palette = "Reds")
```

@@

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 4) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(shape = 4)
```

```{r cache = TRUE}
reset_diff_dat2 <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 1) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(shape = 1)
```

```{r}
reset_diff_dat %>%
  bind_rows(reset_diff_dat2) %>%
  mutate(shape = ifelse(shape == 1, "U", "Triple-U")) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = as.factor(as.integer(name))),
            size = 1) +
  theme_light() +
  labs(col = "Highest order") +
  xlab(expression(log[e] (Effect_size))) +
  scale_color_brewer(palette = "Reds") +
  facet_wrap(~shape)
```
